% Created 2012-11-16 Fri 09:23
\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{fixltx2e}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{float}
\usepackage{wrapfig}
\usepackage{soul}
\usepackage{textcomp}
\usepackage{marvosym}
\usepackage{wasysym}
\usepackage{latexsym}
\usepackage{amssymb}
\usepackage{hyperref}
\tolerance=1000
\usepackage{minted}
\providecommand{\alert}[1]{\textbf{#1}}

\title{Part Five: Application Implementation and Testing}
\author{Weining Zhang}
\date{\today}
\hypersetup{
  pdfkeywords={},
  pdfsubject={},
  pdfcreator={Emacs Org-mode version 7.8.11}}

\begin{document}

\maketitle


\begin{itemize}
\item Total Points: 100
\item Total Weight: 6\%
\item Due: Friday, November 28, 2012, in class
\end{itemize}

\section*{Description}
\label{sec-1}


  In this part, you will implement and test your application
  program. Specifically, your tasks are the following.

\begin{enumerate}
\item PL/SQL Package
     
     You should create a PL/SQL package including at least one
     procedure and one function. These procedures and functions should
     implement some of the application functionality and be used as
     embedded SQL in your application.
\item Application Coding and Testing

     Implement your application program in Java/JDBC, Pro*C/C++, or
     some other language. Specific requirements of the program are
     listed below.
\begin{enumerate}
\item It should implement the functionality specified in the
        conceptual design of the application in ( revised) Part One
        report. Specifically, it should implement functions for data
        update, various predefined or dynamic queries, and business
        rule enforcement.
\item It should provide either a menu driven or a graphical
        (including web) user interface. It should be user-friendly.
\item The program should handle exceptions and errors gracefully.
\item If you program in Pro*C/C++, at lease one subprogram should
        use a cursor (in addition to any cursor used in your PL/SQL
        package). If you program in Java/JDBC, this should be done as
        result sets.
\end{enumerate}
\end{enumerate}
\section*{What to Hand In}
\label{sec-2}

  
  Hand in a well-formatted written final report include following
  items. (I will keep the final report on my file so you should make
  copies for yourselves)

\begin{enumerate}
\item Revised Report of Previous Parts
     
     Since this is the final report, it should be complete. Therefore,
     it should include a fresh copy of revised reports of ALL the
     previous Parts, ordered chronically.
\item Function Lists
     
     A list of originally proposed functions and a list of actually
     implemented functions.
\item Program Source Code

     A script of your PL/SQL package. and a copy of your program
     source code.
\item Script and Screen Shots
     
     Include a script that shows the compilation and execution of your
     program. You should show, within a user session, all functions
     currently supported by your application. If your program provides
     a graphical user interface, include some screen shots as well.
\item Summary Statement of the Entire Project
     
     You should include a section to summarize the team's activities
     during the project; discuss your experiences with this project;
     pros and cons of your design and implementation methodology, and
     aspects of the team work. You should comment on whether and how
     this project contributes towards your learning of database
     subjects and discuss possible future extensions of your
     project. Optionally, you may comment on how each team members
     contributes to the overall project. Please be specific and
     insightful.
\end{enumerate}

\end{document}